Hydras \& Co.

### 2023-07-30 doc/chapter-natural-deduction.tex
corrections chap 12 and 13
corrections chap 13

@@

The deduction theorem (proved in \href{../theories/html/hydras.Ackermann.Deduction.html}{Ackermann.Deduction} is a handy 
tool for proving a proposition $A\arrow B$ by pushing 
the hypothesis $A$ into the context (it corresponds to 
implication introduction in \coq).

@@

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the  proof-tree built
by the proof of the deduction lemma. 
On a fresh branch of the project, please change the definition of
\texttt{SysPrf} and fix the errors this change could cause in the rest of the files. 
\emph{If ensuring compatibility with all the \texttt{Goedel} project is too long and/or difficult, you may just make the changes in separate modules with an ``informative'' \texttt{SysPrf} and limit the compatibility study  to the contents of basic modules like
\texttt{Deduction}, \texttt{folLogic}, etc.
Perhaps you will have to consider other implementation of finite sets of formulas (\emph{e.g.} lists).
}

@@

@@

Let us start with  an implication introduction.

@@

@@

The rest of the proof is composed of basic proof steps, 
and bookkeeping steps (about \texttt{Ensembles.In}).

>>>>

\begin{remark}
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from a proof of $X\sdash f$. We only know that such a proof exists, but cannot get it automatically through a \coq function.
\end{remark}

\begin{project}
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the  proof-tree built
by the proof of the deduction lemma. 
On a fresh branch of the project, please change the definition of
\texttt{SysPrf} and fix the errors this change could cause in the rest of the files. 
\emph{If ensuring compatibility with all the \texttt{Goedel} project is too long and/or difficult, you may just make the changes in separate modules with an ``informative'' \texttt{SysPrf} and limit the compatibility study  to the contents of basic modules like
\texttt{Deduction}, \texttt{folLogic}, etc.
Perhaps you will have to consider other implementation of finite sets of formulas (\emph{e.g.} lists).
}

@@

The deduction theorem (proved in \href{../theories/html/hydras.Ackermann.Deduction.html}{Ackermann.Deduction} is a handy 
tool for proving a proposition $f\arrow g$ by pushing 
the hypothesis $f$ into the context (it corresponds roughly to 
the implication introduction rule in \coq).

@@

@@

\inputsnippets{folLogic/andI}

\inputsnippets{folLogic/andE1, folLogic/andE2}

\inputsnippets{FolExamples/SearchSysPrf}

@@

Let us start with  an implication introduction. The judgement to prove becomes  $(A \arrow B) \arrow A \sdash A$.

@@

\vspace{4pt}

Next goal is $(A \arrow B) \arrow A \sdash \sim\!A \arrow A$.
Please keep in mind  that our current notation system interprets
$\sim\!A \arrow A$ as a disjunction!

@@

The rest of the proof is composed of basic proof steps.
